I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-22 Paper/proofs.tex
fix some typo in proof
update proof

				\qed
			\end{proof}

@@

>>>>

			\end{proof}

@@

			\subsubsection*{From weak to compensating}

			Now, we show Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ is a compensating pair.

			Cut $P,P'$ into segments $P_0,P_1,\cdots$, and $P'_0,P'_1,\cdots$ at each common node; hence each $P_i,P_i'$ have not common nodes, or are the same. Now, for node $a$, there are there cases:
			\begin{itemize}
				\item $a$ is a common nodes.

				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the same sign.

				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the different sign.
			\end{itemize}

			In the last case, $a$ is in a compensating path (the difference is that this path is not from the input to output), and will be open. So we focus on the first and second case.

			For the second case, if we replace $P'$ with $P''=P'_0,\cdots,P'_{i-1},P_{i},P'_{i+1},\cdots$, then $P,P''$ is a weak compensating pair that $a$ is a common nodes. So we only need to consider case 1.

			Therefore, choose a path $Q$ from input to output with nonzero weight that disjoint from $P,P''$. Now, since weights of $P,P''$ have different signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path. This means $a$ will be open.

			Combining all discussion above, if $a$ is in a weak compensating path from input to output, then it is in a compensating path from one layer to another layer. Therefore, Theorem \ref{thm:2} implies Theorem \ref{th2}. This is what we want to show.
